MCC Kids Model Predictions

### 2019-02-11 stats/kids/kids_model_predictions.Rmd
kids noisy model predcitions

ex3_data <- read_csv(file="../data/kids_ex3_data.csv")%>%
  filter(trial != "filler1",trial != "filler2")

@@

var LexiconPrior = Categorical({vs: ["dax = triangle","dax = circle" ], ps: [1, 1]})
'
```

@@

    display(JSON.stringify(ex3Data))

@@

model_pred<- webppl(
  program_code = paste(rsaUtils, rsaModel, modelPredWebppl , sep='\n'),
  data = list(ex3data = ex3_data, modelParams = model_params_by_age),
  data_var = "dataFromR",
  model_var = "predict_by_age",
  chains = 1,
  cores = 4,
  inference_opts = list(method = "MCMC", samples = 10, burn = 1, verbose = T)
)

@@

>>>>

ex3_data <- read_csv(file="../data/kids_ex3_data.csv")%>%
  filter(trial != "filler1",trial != "filler2")%>%
  mutate(binned_age=cut(age_num, breaks=seq.int(3, 5, 0.05), labels=seq.int(0, 1.95, 0.05)))

@@

var LexiconPrior = Categorical({vs: ["dax = triangle","dax = circle" ], ps: [1, 1]})

@@

    //display(JSON.stringify(ex3Data))

@@

model_pred<- webppl(
  program_code = paste(rsaUtils, rsaModel, modelPredWebppl , sep='\n'),
  data = list(ex3data = ex3_data, modelParams = model_params_by_age),
  data_var = "dataFromR"
)

@@

```{r}
ageConditions <- data.frame(
  age_bin = rep(seq.int(0, 1.95, 0.05),4),
  Speaker = c(rep("same_speaker",80),rep("different_speaker",80)),
  Alignment = c(rep("congruent",40),rep("incongruent",40),rep("congruent",40),rep("incongruent",40)))
```

var ex3Data = dataFromR.ex3data
var modelParams = dataFromR.modelParams
var ageConditions = dataFromR.ageConditions

  var model = function(){
    var noise = uniformDrift({a: 0, b:1, width: 0.1})

    var conditionOutput = map(function(conditionInfo){

   var ageConditionSpecificData =  _.filter(ex3Data, {age: conditionInfo.age_bin, Speaker: conditionInfo.Speaker, Alignment: conditionInfo.Alignment})

    map(function(d){ 
      observe(noisyRsaPredictions_diff_cong, d.correct_inf)
    }, ageConditionSpecificData)

  return  [conditionInfo.age_bin + "_" + conditionInfo.Speaker + "_" +  conditionInfo.Alignment, Math.exp(noisyRsaPredictions_diff_cong.score(1))]

}, ageConditions)

```{r}
noisy_model_pred<- webppl(
  program_code = paste(rsaUtils, rsaModel, noisyModelPredWebppl , sep='\n'),
  data =list(ex3data = ex3_data, modelParams = model_params_by_age, ageConditions = ageConditions),
  data_var = "dataFromR",
  model_var = "model",
  chains = 1,
  cores = 4,
  inference_opts = list(method = "MCMC", samples = 10, burn = 2, verbose = T)
)
